---
title: "My Presentation"
author: "Tom Osuchowski"
date: "1/5/2022"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My new slide

```{r, comment= "", echo=TRUE}

head(mtcars)
 plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab="MPG")

```



## My title

Plain text


*italicized text*

**Bold text**

`for (i %in% 1 :10)`

- Bullet one
- Bullet two

1. Item a
2. Item b

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

